Improving Day Ahead Electricity Load Forecasts with Google Trends

### 2014-08-15 Paper/DraftPaper.Rnw
Trying to get the new data in and working.

<<echo=false,results=hide>>=
WTrendsLimited<-WTrends[!is.na(WTrends$Weather),]

@@

<<echo=false,results=hide>>=
HourModel<-function(hour){
  Hour<-formatC(hour, width=2, flag="0")
  as.formula(paste("HE",Hour,"~ F",Hour,"+Weather",sep='' ))}

>>>>

<<echo=false,results=hide>>=
WTrends$Weekend<-weekdays(as.Date(WTrends$Date)) %in% c('Saturday','Sunday')
WTrendsLimited<-WTrends[!is.na(WTrends$Weather),]

@@

<<echo=false,results=hide>>=
HourModel<-function(hour){
  Hour<-formatC(hour, width=2, flag="0")
  as.formula(paste("HE",Hour,"~ F",Hour,"+Weather:Weekend",sep='' ))}
